### 2024-04-09 README.qmd
Update results

As shown in the graph above, some records (`r round(nrow(d_offence) / nrow(d_all) * 100, 1)`%) have missing values for the 'offence' column (these records did not classify as an offence). 
Many records lack either an offence or a location (`r round(nrow(d) / nrow(d_all) * 100, 1)`%).
Filtering these out leaves `r nrow(d)` complete records.

There are `r unique(d$location) |> length()` unique locations in the data, with the most common locations shown below:

@@

The results show there is one outlier with a very high number of crashes. We can remove this and plot the data again:

```{r}
raster_count_no_outlier = raster_count |>
  clamp(-Inf, 100)
plot(raster_count_no_outlier)
```

>>>>

As shown in the graph above, `r round(nrow(d_offence) / nrow(d_all) * 100, 1)`% have values for the 'offence' column. 
Many records lack either an offence or a location, leaving only `r round(nrow(d) / nrow(d_all) * 100, 1)`% or `r nrow(d)` complete records.

There are `r unique(d$location) |> length()` unique location text strings (addresses) in the data, with the most common locations shown below:

@@

<!-- The results show there is one outlier with a very high number of crashes. We can remove this and plot the data again: -->

```{r}
# raster_count_no_outlier = raster_count |>
#   clamp(-Inf, 100)
# plot(raster_count_no_outlier)
```
